Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)

### 2025-08-13 analysis/paper/paper.qmd
uupdate basic assemblage details figures

p_raw_material <- 
ggplot(df_long %>% 
         mutate(category = case_when(
           category == "cores" ~ "Cores",
           category == "spheroids" ~ "Spheroid",
           category == "total" ~ "Total",
           category == "Polys_and_Multi_cores" ~ "Polys and Multi cores"
           )), 
       aes(x = material, 
           y = prop, 
           fill = category)) +
  geom_col(position = position_dodge(width = 0.6), width = 0.5) +
  labs(
    x = "",
    y = "Percentage (%)",
    fill = "Technological Type"
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
    scale_fill_manual(values = c(
    "Spheroid" = "orange", 
    "Polys and Multi cores" = "#66c2a5",
    "Cores" = "lightgray", 
    "Total" = "gray"
  )) +
  theme_minimal(base_size = 8) +
  theme(
    legend.position = c(0.95, 0.95),              
    legend.justification = c("right", "top"),      
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),  
    legend.box.background = element_rect(color = "black")  
  )
p_raw_material

@@

# 画图
p_dimensions <- 
ggplot(long_data, aes(x = metric, y = value, fill = artifact)) +
  geom_boxplot(position = position_dodge(0.8), width = 0.5) +
  labs(
    x = "",
    y = "Measurement (mm)",
    fill = "Technological Type"
  ) +
  scale_fill_manual(values = c(
    "Cores" = "lightgray", 
    "Spheroid" = "orange", 
    "Polys and Multi cores" = "#66c2a5"
  )) +
  theme_minimal(base_size = 8) +
  theme(
    legend.position = c(0.95, 0.95),       
    legend.justification = c("right", "top"),  
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA), 
    legend.box.background = element_rect(color = "black")  
  )

p_dimensions
```

>>>>

p_raw_material <- 
ggplot(df_long %>% 
         mutate(category = case_when(
           category == "cores" ~ "Cores",
           category == "spheroids" ~ "Spheroid",
           category == "total" ~ "Total",
           category == "Polys_and_Multi_cores" ~ "Polys and Multi cores"
           )) %>% 
         filter(category != "Total"), 
       aes(x = material, 
           y = prop, 
           fill = category)) +
  geom_col(position = position_dodge(width = 0.6), width = 0.5) +
  labs(
    x = "",
    y = "Percentage (%)",
    fill = "Technological Type"
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
    scale_fill_manual(values = c(
    "Spheroid" = "orange", 
    "Polys and Multi cores" = "#66c2a5",
    "Cores" = "lightgray"
  )) +
  theme_minimal(base_size = 8) +
  theme(
    legend.position = c(0.80, 0.95),              
    legend.justification = c("right", "top"),      
    legend.background = element_rect(fill = alpha("white", 0.6), color = NA),  
    legend.box.background = element_rect(color = "black")  
  )

@@

# 画图
p_dimensions <- 
ggplot(long_data, aes(x = metric, y = value, fill = artifact)) +
  geom_boxplot(position = position_dodge(0.8), width = 0.5) +
  labs(
    x = "",
    y = "Measurement (mm)",
    fill = "Technological Type"
  ) +
  scale_fill_manual(values = c(
    "Cores" = "lightgray", 
    "Spheroid" = "orange", 
    "Polys and Multi cores" = "#66c2a5"
  )) +
  theme_minimal(base_size = 8) +
  guides(fill = "none")
